---
output:
  html_document:
    toc: TRUE
    toc_float: TRUE 
    theme: cosmo
    highlight: pygments
---
```{r setup, message=FALSE,echo = FALSE, warning=FALSE}
library(data.table)
library(tidyverse)
library(dplyr)
library(plotly)
library(DT)
library(knitr)
# Initialize code chunk options
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  eval=TRUE,
  echo = FALSE,
  cache = FALSE,
  fig.align = 'center',
  class.source = "code-r")
```


```{r load-data, include=FALSE}
start_time <- Sys.time()
source("process_project_data.R")
end_time <- Sys.time()
end_time - start_time
```

```{r,echo=FALSE}
num_commits_plot <- msg_time %>% group_by(repo, year) %>% summarize(count = n()) %>% 
  ggplot(aes(x = year, y=count, color=repo)) + 
  geom_point() +
  geom_line() +
  theme(legend.spacing.x  = unit(0.01, "cm")) +
  theme_ipsum() +
  theme(legend.text = element_text(size = 6, face = "bold"),
        legend.position = "top", 
        legend.key.height = unit(0.1, "cm"),
        legend.key.width = unit(0.2, "cm")) +
  ggtitle("Number of commits of most popular repos on Github over years")
p1 <- ggplotly(num_commits_plot)
```
```{r,echo=FALSE}
dow_plot <- msg_time %>% group_by(repo, day_of_week) %>% 
  ggplot(aes(x = day_of_week, fill=repo)) + 
  geom_bar() +
  theme(legend.spacing.x  = unit(0.01, "cm")) +
  theme_ipsum() +
  theme(legend.text = element_text(size = 6, face = "bold"),
        legend.position = "top", 
        legend.key.height = unit(0.1, "cm"),
        legend.key.width = unit(0.2, "cm")) +
  ggtitle("Number of commits for each Day of Week")
p2 <- ggplotly(dow_plot)
```
```{r,echo=FALSE}
tokens_count_graph <-  msg_tokens %>% 
  top_n(20, n) %>% 
  ggplot(aes(n, fct_reorder(tokens, n))) + 
  geom_col(aes(fill = tokens)) + 
  scale_colour_brewer(palette = "Spectral") +
  labs(y = "Tokens", x = "count") +
  guides(fill = "none") +
  ggtitle("Top 20 most frequent tokens in commit messages across all repos")
p3 <- ggplotly(tokens_count_graph)
```
```{r}
num_commits_plot2 <- msg_time %>% filter(year > 2007 | (year == 2007 & month %in% c("Oct", "Nov", "Dec"))) %>% group_by(repo, year) %>% summarize(count = n()) %>% 
  ggplot(aes(x = year, y=count, color=repo)) + 
  geom_point() +
  geom_line() +
  theme(legend.spacing.x  = unit(0.01, "cm")) +
  theme_ipsum() +
  theme(legend.text = element_text(size = 6, face = "bold"),
        legend.position = "top", 
        legend.key.height = unit(0.1, "cm"),
        legend.key.width = unit(0.2, "cm")) +
  ggtitle("Number of commits of most popular repos since Github Development")
p4 <- ggplotly(num_commits_plot2)
```

## Interactive tables of the raw/processed datasets{.tabset}

Below we showcasing some important dataframes that are used throughout of this project and that are hard to fit in the report, this includes (1) both raw datasets, (2) Cleaned `personal` dataset (3) Processed datasets for time series and natural language processing.

### Raw Commit Message

```{r, include=TRUE}
# Head the first 7 rows
datatable(
  head(com_msg, 7), 
  options = list(
    scrollX = TRUE, 
    scrollY = FALSE,
    paging = FALSE,
    dom = 't'
  ),
  rownames = FALSE,
  caption = "Table 1 - Top 7 rows of the raw dataset commit messages"
) %>%
formatStyle(
  columns = 1:5,
  border = "1px solid black"
)
```

### Raw `WilliamQD` repository data

```{r, include=TRUE}
datatable(
  head(commit_df, 30), 
  options = list(
    pageLength = 10,
    lengthMenu = c(10, 20, 30)
  ),
  rownames = FALSE,
  caption = "Table 2 - Top 30 rows of the raw dataset scraped from Github under the account WilliamQD"
) %>%
formatStyle(
  columns = 1:4,
  border = "1px solid black"
)
```

### Cleaned `WilliamQD` repository data

```{r, include=TRUE}
datatable(
  head(commit_df_clean, 30), 
  options = list(
    scroll.X = TRUE,
    scroll.Y = FALSE,
    paging = TRUE,
    pageLength = 10,
    lengthMenu = c(10, 20, 30)
  ),
  rownames = FALSE,
  caption = "Table 3 - Top 30 rows of cleaned dataset of commit messages from account WilliamQD"
) %>%
formatStyle(
  columns = 1:4,
  border = "1px solid black"
)
```

### Dataframe modefied for Time series 
```{r, include=TRUE}
datatable(
  head(msg_time, 5), 
  options = list(
    scroll.X = TRUE,
    scroll.Y = FALSE,
    paging = FALSE
  ),
  rownames = FALSE,
  caption = "Table 4 - Top 5 rows of the commit message dataset with time variables"
) %>%
formatStyle(
  columns = 1:7,
  border = "1px solid black"
)
```

### Tokenized Commit Message

```{r, include=TRUE}
datatable(
  head(msg_token_byrepo_percent, 30), 
  options = list(
    scroll.X = TRUE,
    scroll.Y = FALSE,
    paging = TRUE,
    pageLength = 10,
    lengthMenu = c(10, 20, 30)
  ),
  rownames = FALSE,
  caption = "Table 6 - Tokenized commit message with percentage, calculated based on each repo"
) %>%
formatStyle(
  columns = 1:5,
  border = "1px solid black"
)
```

## {-}


## Interactive plots{.tabset}

Below are interactive plots created for visualization and analysis. The first three are based on some kind of time variable, such that we analyze how number of commits changes or behaviors as time changes. The last one is simply a count of most popular token in the commit messages. For a more informative visualization of the language part, I encourage to check the animated wordcloud or the report itself.

### Number of Commits starting 1970

```{r echo=FALSE}
p1
```

### Number of Commits starting Oct 2007

```{r}
p4
```

### Commits in each Day of Week

```{r echo=FALSE}
p2
```

### Most Frequent Tokens
```{r echo=FALSE}
p3
```

## {-}