---
output:
  html_document:
    theme: cosmo
    highlight: pygments
---
```{r setup, message=FALSE,echo = FALSE, warning=FALSE}
library(data.table)
library(tidyverse)
library(dplyr)
library(plotly)
library(DT)
library(knitr)
# Initialize code chunk options
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  eval=TRUE,
  echo = FALSE,
  cache = FALSE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618,
  out.width = "700px",
  class.source = "code-r")
```


```{r load-data, include=FALSE}
start_time <- Sys.time()
source("process_project_data.R")
end_time <- Sys.time()
end_time - start_time
```

```{r,echo=FALSE}
num_commits_plot <- msg_time %>% group_by(repo, year) %>% summarize(count = n()) %>% 
  ggplot(aes(x = year, y=count, color=repo)) + 
  geom_point() +
  geom_line() +
  theme(legend.spacing.x  = unit(0.01, "cm")) +
  theme_ipsum() +
  theme(legend.text = element_text(size = 6, face = "bold"),
        legend.position = "top", 
        legend.key.height = unit(0.1, "cm"),
        legend.key.width = unit(0.2, "cm")) +
  ggtitle("Number of commits of most popular repos on Github over years")
p1 <- ggplotly(num_commits_plot)
```
```{r,echo=FALSE}
dow_plot <- msg_time %>% group_by(repo, day_of_week) %>% 
  ggplot(aes(x = day_of_week, fill=repo)) + 
  geom_bar() +
  theme(legend.spacing.x  = unit(0.01, "cm")) +
  theme_ipsum() +
  theme(legend.text = element_text(size = 6, face = "bold"),
        legend.position = "top", 
        legend.key.height = unit(0.1, "cm"),
        legend.key.width = unit(0.2, "cm")) +
  ggtitle("Number of commits for each Day of Week")
p2 <- ggplotly(dow_plot)
```
```{r,echo=FALSE}
tokens_count_graph <-  msg_tokens %>% 
  top_n(20, n) %>% 
  ggplot(aes(n, fct_reorder(tokens, n))) + 
  geom_col(aes(fill = tokens)) + 
  scale_colour_brewer(palette = "Spectral") +
  labs(y = "Tokens", x = "count") +
  guides(fill = "none") +
  ggtitle("Top 20 most frequent tokens in commit messages across all repos")
p3 <- ggplotly(tokens_count_graph)
```
## Interactive tables of the raw/processed datasets{.tabset}

Below we showcasing some important dataframes that are used throughout of this project and that are hard to fit in the report, this includes (1) both raw datasets, (2) Cleaned `personal` dataset (3) Processed datasets for time series and natural language processing.

### Raw Commit Message

```{r, include=TRUE}
# Head the first 7 rows
datatable(
  head(com_msg, 7), 
  options = list(
    scrollX = TRUE, 
    scrollY = FALSE,
    paging = FALSE,
    dom = 't'
  ),
  rownames = FALSE,
  caption = "Table 1 - Top 7 rows of the raw dataset commit messages"
) %>%
formatStyle(
  columns = 1:5,
  border = "1px solid black"
)
```

### Raw `WilliamQD` repository data

```{r, include=TRUE}
datatable(
  head(commit_df, 30), 
  options = list(
    pageLength = 10,
    lengthMenu = c(10, 20, 30)
  ),
  rownames = FALSE,
  caption = "Table 2 - Top 30 rows of the raw dataset scraped from Github under the account WilliamQD"
) %>%
formatStyle(
  columns = 1:4,
  border = "1px solid black"
)
```

### Cleaned `WilliamQD` repository data

```{r, include=TRUE}
datatable(
  head(commit_df_clean, 30), 
  options = list(
    scroll.X = TRUE,
    scroll.Y = FALSE,
    paging = TRUE,
    pageLength = 10,
    lengthMenu = c(10, 20, 30)
  ),
  rownames = FALSE,
  caption = "Table 3 - Top 30 rows of cleaned dataset of commit messages from account WilliamQD"
) %>%
formatStyle(
  columns = 1:4,
  border = "1px solid black"
)
```

### Dataframe modefied for Time series 
```{r, include=TRUE}
datatable(
  head(msg_time, 5), 
  options = list(
    scroll.X = TRUE,
    scroll.Y = FALSE,
    paging = FALSE
  ),
  rownames = FALSE,
  caption = "Table 4 - Top 5 rows of the commit message dataset with time variables"
) %>%
formatStyle(
  columns = 1:7,
  border = "1px solid black"
)
```

### Tokenized Commit Message

```{r, include=TRUE}
datatable(
  head(msg_token_byrepo_percent, 30), 
  options = list(
    scroll.X = TRUE,
    scroll.Y = FALSE,
    paging = TRUE,
    pageLength = 10,
    lengthMenu = c(10, 20, 30)
  ),
  rownames = FALSE,
  caption = "Table 6 - Tokenized commit message with percentage, calculated based on each repo"
) %>%
formatStyle(
  columns = 1:5,
  border = "1px solid black"
)
```

## {-}


## Below are interactive plots for Assignment 5 {.tabset}

### Figure 1

```{r echo=FALSE}
p1
```

### Figure 2

```{r echo=FALSE}
p2
```

### Figure 3
```{r echo=FALSE}
p3
```

## {-}

You can also check the "Animated plots" tab for animated plots I created.